Supervised Reinforcement Learning with Partial States: \\ a Teaching Method for Action Selection for HRI

### 2017-07-26 paper.tex
removing weirdly formulated sentence
Reorganisation

When selecting an action, the agent can also use
the dimensions of the close state $s'$ used for the selection to indicate the
supervisor which parts of the state have been used for the action selection.

@@

An example of an application is a social robot which interacts with children in an educational scenario.
The robot plays an educational game with children to teach them notions about
diverse topics according to the needs of the teacher. For this example, a child
and a robot are playing a game about the food web, teaching wich animals eat which
ones on a Sandtray~\cite{baxter2012touchscreen}. In addition to the child and
the robot, an adult supervises the robot using a tablet with a Graphical User
Interface (GUI) to teach the robot how to interact with the child as shown in
Figure~\ref{fig:setup}.
\begin{figure}
        \centering
  \includegraphics[width=60mm]{./figs/setup} 
    \caption{Interaction setup: the child and the robot are interacting on the
    touchscreen and a supervisor can control the robot using a GUI on a tablet.}
        \label{fig:setup}
\end{figure}

The GUI (shown in Figure \ref{fig:gui} is an augmented
version of the game itself, which can be use to make the robot move items on the
game by dragging them on the GUI or which can display actions proposed by the
robot with a cancel button to refuse an action. For example in
Figure~\ref{fig:gui} the robot proposes to move the eagle to the rat, and
highlight (as shown by blue circles) the eagle and the rat. This indicate that
features relevant to the eagle and the rat have been used to select this action.

>>>>

%When selecting an action, the agent can also use
%the dimensions of the close state $s'$ used for the selection to indicate the
%supervisor which parts of the state have been used for the action selection.

@@

\begin{figure}
        \centering
  \includegraphics[width=60mm]{./figs/setup} 
    \caption{Interaction setup: the child and the robot are interacting on the
    touchscreen and a supervisor can control the robot using a GUI on a tablet.}
        \label{fig:setup}
\end{figure}

An example of an application is a social robot which interacts with children in an educational scenario.
The robot plays an educational game with children to teach them notions about
diverse topics according to the needs of the teacher. For this example, a child
and a robot are playing a game about the food web, teaching wich animals eat which
ones on a Sandtray~\cite{baxter2012touchscreen}. In addition to the child and
the robot, an adult supervises the robot using a tablet with a Graphical User
Interface (GUI) to teach the robot how to interact with the child as shown in
Figure~\ref{fig:setup}.

The GUI (Figure \ref{fig:gui}) is an augmented
version of the game itself, which can be use to make the robot move items on the
game by dragging them on the GUI or which can display actions proposed by the
robot with a cancel button to refuse an action. For example in
Figure~\ref{fig:gui} the robot proposes to move the eagle to the rat, and
highlight (as shown by blue circles) the eagle and the rat. This indicate that
features relevant to the eagle and the rat have been used to select this action.
